---
title: "hw2"
author: "Hao Zheng(hz2772)"
date: "10/3/2021"
output: html_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(readxl)
library(tidyr)
library(ggplot2)
library(ggthemes)
```

**Problem 1**
```{r, message = FALSE, results='hide'}
trash_data = 
  read_excel("data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",
             sheet = "Mr. Trash Wheel"
             ) %>%
  janitor::clean_names() %>%
  select(dumpster:homes_powered) %>%
  drop_na(dumpster) %>%
  mutate(sports_balls=round(sports_balls))

precip18_data = 
  read_excel("data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",
             sheet = "2018 Precipitation",
             range = "A2:B14") %>%
  janitor::clean_names() %>%
  tidyr::drop_na(total) %>%
  mutate(year = 2018)

precip19_data = 
  read_excel("data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",
             sheet = "2019 Precipitation",
             range = "A2:B14") %>%
  janitor::clean_names() %>%
  tidyr::drop_na(total) %>%
  mutate(year = 2019) 

precip_data = 
  union(precip18_data,precip19_data) %>%
  pivot_wider(names_from = "year",
              values_from = "total") %>%
  mutate(month=month.name)
## description
skimr::skim(trash_data)
skimr::skim(precip_data)
```
The **"Trash-Wheel"** dataframe has 454  rows and 14 columns which are 14 variables named dumpster, month, year and etc. Like the number of glass bottles in the dumpster 1 in May is `r trash_data %>% filter(dumpster==1 & month=="May") %>% pull(glass_bottles)`. The **median number of sports balls in dumpster of 2019** is `r median(trash_data %>% filter(year==2019) %>% pull(sports_balls))`.


The **precipitation** dataframe of 2018 and 2019 has 12 rows and 3 columns which are 3 variables named month, 2018 and 2019. The values are precipitation data of each month. Like the precipitation data in May of 2018 is `r precip_data %>% filter(month=="May") %>% pull("2018")`. The **total precipitation of 2018** is `r sum(select(precip_data,"2018"))`.


**Problem2**
```{r, message = FALSE, warning=FALSE, results='hide'}
pm_df = read.csv("data/fivethirtyeight_datasets/pols-month.csv") %>%
  separate(col=mon,into = c("year","month","day"),sep = "-") %>%
  mutate(month=replace(month,month==c("01","02","03","04","05","06","07","08","09","10","11","12"),month.name)) %>%
  mutate(president=prez_gop+prez_dem) %>%
  select(-prez_dem)  %>%
  select(-prez_gop)  %>%
  select(-day) %>%
  mutate(year=as.integer(year))

snp_df = read.csv("data/fivethirtyeight_datasets/snp.csv") %>%
  separate(col=date,into = c("month","day","year"),sep = "/") %>%
  mutate(month = month.name[as.integer(month)]) %>%
  select(year,month,everything()) %>%
  mutate(year = ifelse(as.integer(year)>=50,as.integer(year)+1900,as.integer(year)+2000)) 

une_df = read.csv("data/fivethirtyeight_datasets/unemployment.csv") %>%
  pivot_longer(Jan:Dec,
               names_to="month",
               values_to="une_data") %>%
  rename(year=Year) %>%
  mutate(month=replace(month,month==month.abb,month.name))

mer_df = merge(x=snp_df,y=pm_df,by=c("year","month"),all.y = TRUE) 
mer_df = merge(x=une_df,y=mer_df,by.x=c("year","month"),all.y = TRUE)

skimr::skim(pm_df)
skimr::skim(snp_df)
skimr::skim(une_df)
```
**The pols-month data** has 822 rows and 9 columns, with 9 variables named month, year, gov_gop and etc. The values are from each year and each month from 1947 to 2015. Like the gov_gop value in May of 1998 is `r pm_df %>% filter(year==1998,month=="May") %>% pull(gov_gop)`.


**The snp data** has 787 rows and 4 columns, with 4 variables named month, day, year and close. The values are from each year and each month from 1950 to 2015. Like the close value in May of 1998 is `r snp_df %>% filter(year==1998,month=="May") %>% pull(close)`.


**The unemployment data** has 816 rows and 3 columns, with 3 variables named month, year and une_data. The values are from each year and each month from 1948 to 2015. Like the unemployment value in May of 1998 is `r une_df %>% filter(year==1998,month=="May") %>% pull(une_data)`.


**Problem 3**
```{r, message = FALSE, warning=FALSE}
pbn_df = read_csv("data/Popular_Baby_Names.csv") 
pbn_df = pbn_df[!duplicated(pbn_df),] %>%
  janitor::clean_names() %>%
  ## find some ethnicity categories changed
  mutate(ethnicity=replace(ethnicity,ethnicity=="ASIAN AND PACI","ASIAN AND PACIFIC ISLANDER")) %>%
  mutate(ethnicity=replace(ethnicity,ethnicity=="BLACK NON HISP","BLACK NON HISPANIC")) %>%
  mutate(ethnicity=replace(ethnicity,ethnicity=="WHITE NON HISP","WHITE NON HISPANIC")) 
         

olv_df = filter(pbn_df,childs_first_name=="Olivia",gender=="FEMALE") %>%
  select(-gender,-childs_first_name,-count) %>%
  pivot_wider(names_from = "year_of_birth",
              values_from = "rank")
olv_df

pop_male_df = filter(pbn_df,gender=="MALE",rank==1) %>%
  select(-gender,-count,-rank) %>%
  pivot_wider(names_from = "year_of_birth",
              values_from = "childs_first_name")

plot_df = filter(pbn_df,year_of_birth==2016,gender=="MALE",ethnicity=="WHITE NON HISPANIC") 
pop_male_df

ggplot(plot_df,aes(x=rank,y=count)) + 
  geom_point(alpha=.5,color=rainbow(length(rank)))+
  ggtitle("Numbers of 2016 Rank Popular Male Name")+
  theme_pander()
```


